Reconstructing Propositional Proofs in Type Theory

### 2017-10-25 paper/sections/metis-language-and-proofs.tex
Fixed citation.
Fixed citations.

\Metis is an automatic theorem prover written in \len{ML}
for first-order logic with equality developed by John Hurd
\cite{hurd2003first}. This prover is suitable for proof
reconstruction since it provides well-documented proofs
to justify its deduction steps from the basis of only six inference
rules. In Fig.~\ref{fig:metis-inferences}, we show the three \Metis
rules for propositional logic.

>>>>

\Metis is an automatic theorem prover written in \len{ML} for
first-order logic with equality developed by
\citeauthor{hurd2003first}~\cite{hurd2003first}. This prover is
suitable for proof reconstruction since it provides well-documented
proofs to justify its deduction steps from the basis of only six
inference rules. In Fig.~\ref{fig:metis-inferences}, we show the three
\Metis rules for propositional logic.
